### 2012-06-25 inst/examples/figure3.Rmd
figure3

  SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=2e4)
  opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                       profit, delta, reward=0)
}
````

@@

``` {r sethiplots, rerun=TRUE}
require(reshape2)
policy <- melt(data.frame(stock = x_grid, det = det$D[,1], low=low$D[,1],
               g = g$D[,1], m = m$D[,1], i= m$D[,1], 
               gm = gm$D[,1], gi = gi$D[,1], mi = mi$D[,1], gmi = gmi$D[,1]), 
               id = "stock")

ggplot(policy) + 
  geom_point(aes(stock, stock-x_grid[value], color=variable)) +
	geom_smooth(aes(stock, stock-x_grid[value], color=variable)) +
  ylab("escapement")

ggplot(policy) +
  geom_point(aes(stock, x_grid[value], color=variable)) +
	geom_smooth(aes(stock, x_grid[value], color=variable)) +
  ylab("harvest")

value <- melt(data.frame(stock = x_grid, det=det$V, low = low$V, 
                         g = g$V, m = m$V, gm = gm$V, 
                         gi = gi$V, mi=mi$V, gmi = gmi$V), id = "stock")

ggplot(value) + 
  geom_point(aes(stock, value, color=variable)) +
  geom_smooth(aes(stock, value, color=variable)) +
  ylab("Net Present Value")
````

## Simulations

``` {r simfn, rerun=TRUE} 
simulatereps <- function(opt, true_g, true_m, true_i){

  z_g <- function() 1+(2*runif(1, 0,  1)-1) * true_g
  z_m <- function() 1+(2*runif(1, 0,  1)-1) * true_m
  z_i <- function() 1+(2*runif(1, 0,  1)-1) * true_i

  sims <- lapply(1:100, function(i){
    ForwardSimulate(f, pars, x_grid, h_grid, x0 = K, opt$D, z_g, z_m, z_i, profit)
  })

  sims
}
````

All cases

``` {r runallsims, dependson="simfn"} 
policyfn <- list(det=det, low=low, g=g, m=m, i=i, gm=gm, gi=gi, mi=mi, gmi=gmi)
noise <- list( det  = c(0,0,0),        low = c(0.1, .1, .1),  growth = c(lvl, 0, 0),
               measure  = c(0, lvl, 0),implement = c(0,0,lvl),growth_measure = c(lvl, lvl, 0), 
               growth_implement = c(lvl, 0, lvl),  measure_implement = c(0, lvl, lvl), all = c(lvl, lvl, lvl)) 
allcases <- lapply(policyfn, function(policyfn_i){
  lapply(noise, function(noise_i){
    simulatereps(policyfn_i, noise_i[1], noise_i[2], noise_i[3])
  })
})
````

``` {r tidyall, dependson="runallsims"}
sims <- unlist(allcases, recursive=FALSE)
dat <- melt(sims, id=names(sims[[1]][[1]]))  
dt <- data.table(dat)
setnames(dt, c("L2", "L1"), c("reps", "uncertainty")) # names are nice
````

### Plots

``` {r  onerep, dependson="tidyall"}
ggplot(subset(dt,reps==1)) +
  geom_line(aes(time, fishstock)) +
  geom_line(aes(time, harvest), col="darkgreen") + 
  facet_wrap(~uncertainty) 
````

This plot summarizes the stock dynamics by visualizing the replicates.

``` {r stock, fig.cap="the induced dynamics in the stock size over time, for all replicates, by scenario", dependson="tidyall"}
p1 <- ggplot(subset(dt, fishstock>0)) 
p1 + geom_line(aes(time, fishstock, group = reps), alpha = 0.1) + facet_wrap(~uncertainty)
````

``` {r profits, fig.cap="the distribution of profits by scenario", dependson="tidyall"}
profits <-dt[ , sum(profit), by=c("reps", "uncertainty")] 
ggplot(profits) + geom_histogram(aes(V1)) + facet_wrap(~uncertainty)
````

Summary statistics

``` {r summarystats, cache=FALSE}
means <- profits[, mean(V1), by=uncertainty]
sds <- profits[, sd(V1), by=uncertainty]
````

``` {r prettytable, cache=FALSE, results="asis"}
require(xtable)
uncertainties <- names(noise) 
print(xtable(matrix(means$V1, nrow=length(noise), dimnames=list(uncertainties, uncertainties))), type="html")
print(xtable(matrix(sds$V1, nrow=length(noise), dimnames=list(uncertainties, uncertainties))), type="html")
````

# References

``` {r biblio, echo=FALSE, results="asis"}
knitcitations::bibliography("html")
````

>>>>

  SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=2e5)
  opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                       profit, delta, reward=0)
}
````

@@

``` {r sethiplots, rerun=TRUE}
require(reshape2)
policy <- melt(data.frame(stock = x_grid, det = det$D[,1], low=low$D[,1],
               g = g$D[,1], m = m$D[,1], i= i$D[,1], 
               gm = gm$D[,1], gi = gi$D[,1], mi = mi$D[,1], gmi = gmi$D[,1]), 
               id = "stock")
policy <- melt(data.frame(stock = x_grid, low=low$D[,1],
               g = g$D[,1], m = m$D[,1], i= i$D[,1]), 
               id = "stock")

ggplot(policy) + 
#  geom_point(aes(stock, stock-x_grid[value], color=variable)) +
	geom_smooth(aes(stock, stock-x_grid[value], color=variable)) +
  ylab("escapement") 
```
